Publilia-03-survivorship.Rmd

### 2023-08-11 scripts/Publilia-03-survivorship.Rmd
converted offspring survivorship modeling workflow to functions

### Model fitting and confidence intervals and plotting functions
```{r}
### fit survivorship model
fit_surv <- function(data_in, survNom, survDen, tenure, 
                     treatment, vis, interaction=c("full","pw")){
  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))

  mai.b <- eval(substitute(glm(survNom/survDen ~ 
            tenure*treatment,
          data = data, weights = survDen, family = binomial)))
  print("Interaction, Binomial: ")
  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

  mai.qb <- eval(substitute(glm(survNom/survDen ~ 
            tenure*treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  ma.qb <- eval(substitute(glm(survNom/survDen ~ 
            tenure+treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("No Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

@@

# Example
# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)

### fit survivorship model
fit_surv_quad <- function(data_in, survNom, survDen, tenure, 
                     treatment){
  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))

  mai.b <- eval(substitute(glm(survNom/survDen ~
            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
          data = data, weights = survDen, family = binomial)))
  print("Interaction, Binomial: ")
  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

  mai.qb <- eval(substitute(glm(survNom/survDen ~
            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  ma.qb <- eval(substitute(glm(survNom/survDen ~
            tenure+treatment + (I(as.numeric(tenure)^2))*treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("No Interaction, Quasibinomial: ")
  print(capture.output(summary(ma.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(ma.qb))))-1)])

# Example
# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
#                  survNom=n_hatched, survDen=med_t5eggs)

@@

  data <- eval(substitute(
    data_in %>% filter(!is.na(tenure)) %>%
      select(location, tenure, treatment, survDen, survNom) %>%
      add_column(fit = predict(model, newdata = ., type = 'response'))
    ))

@@

@@

# Example
# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants, 
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
# 
# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants, 
#                  survNom=n_hatched, survDen=med_t5eggs,
#                  model = test_fits.pw$mai.qb)

### Plot model results with confidence intervals
plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
  (eval(substitute(plot <- ggplot(data = ci_data, 
       aes(x = tenure, y = fit, 
           color = treatment, fill = treatment)) +
    theme_publilia() +
    geom_point(aes(y = survNom/survDen), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect))))
#
}

# Example
# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
# 
# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants,
#                  survNom=n_hatched, survDen=med_t5eggs,
#                  model = test_fits.pw$mai.qb)
# 
# (p <- plot_ci(ci_data = test_ci_data, tenure = des, treatment=ants,
#              survNom = n_hatched, survDen = med_t5eggs) +
#     xlab("Latest desertion date relative to hatch") +
#     ylab("Hatching success") +
#     scale_color_manual(values = c("brown1", "black")) +
#     scale_fill_manual(values = c("brown1", "black")))
# summary(test_fits.pw$mai.qb)
```

# Supp 1 -`desL * ants_treatment * desL^2`
## Figures
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

# egg survivorship
des_Esurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_Esurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ant_treatment.quad.fits$mai.qb)

des_Esurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion"))

(desL.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ant_treatment.quad.final.png",
       desL.ant_treatment.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

@@

```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

## Figures
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_hatch.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_gt2d)

des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))

(desL.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ants_gt2d.quad.final.png",
       desL.ants_gt2d.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

# Supp 2 -`desP * ants_gt2 * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=desP, treatment=ants_gt2d)

des_hatch.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ants_gt2d.quad.fits$mai.qb)

des_hatch.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=desP, treatment=ants_gt2d)

des_Nsurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=desP, treatment=ants_gt2d)

des_Esurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desP.ants_gt2d.quad.fits$mai.qb)

des_Esurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))

(desP.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ants_gt2d.quad.final.png",
       desP.ants_gt2d.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

# Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=desP, treatment=ant_treatment)

des_hatch.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ant_treatment.quad.fits$mai.qb)

des_hatch.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=desP, treatment=ant_treatment)

des_Nsurv.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

>>>>

### Model fitting and confidence intervals and plotting functions
```{r}
### fit survivorship model
fit_surv <- function(data_in, survNom, survDen, tenure, treatment, quad){
  data <- data_in %>% filter(!is.na(.[[tenure]]))

  if (!quad) {
    formula.mai <- paste0(survNom,"/",survDen,"~",tenure,"*",treatment) %>% as.formula()
    formula.ma <- paste0(survNom,"/",survDen,"~",tenure,"+",treatment) %>% as.formula()
  } else if (quad) {
    formula.mai <- paste0(
      survNom,"/",survDen,"~",
      tenure,"*",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
      ) %>% as.formula()
    formula.ma <- paste0(
      survNom,"/",survDen,"~",
      tenure,"+",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
    ) %>% as.formula()
  }

  mai.b <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = binomial)
  print("Interaction, Binomial: ")
  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

  mai.qb <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = quasibinomial)
  print("Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  ma.qb <- glm(formula = formula.ma, data = data, weights = data[[survDen]], family = binomial)
  print("No Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

@@

@@

  data <- data_in %>%
    filter(!is.na(.data[[tenure]])) %>%
    select(location, all_of(tenure), all_of(treatment), all_of(survDen), all_of(survNom)) %>%
    add_column(fit = predict(model, newdata = ., type = 'response'))

@@

  ## add fit and se.fit on the **link** scale
  data_fit_link <- data %>% 
    add_column(
      predict(model, data, se.fit = TRUE)[1:2] %>% 
        as_tibble() %>%
        setNames(c('fit_link','se_link'))) %>%
    ## create the interval and backtransform
    mutate(fit_resp  = ilink(.data$fit_link),
           conf_upr = ilink(.data$fit_link + (2 * .data$se_link)),
           conf_lwr = ilink(.data$fit_link - (2 * .data$se_link)))

@@

# Example
# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
# 
# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs",
#                  model = test_fits$mai.qb)

### Plot model results with confidence intervals
plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
  plot <- ggplot(data = ci_data, 
       aes(x = .data[[tenure]], y = fit, 
           color = .data[[treatment]], fill = .data[[treatment]])) +
    theme_publilia() +
    geom_point(aes(y = .data[[survNom]]/.data[[survDen]]), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect)
}

# Example
# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
# 
# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs",
#                  model = test_fits$mai.qb)
# 
# (p <- plot_ci(ci_data = test_ci_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs") +
#     xlab("Latest desertion date relative to hatch") +
#     ylab("Hatching success") +
#     scale_color_manual(values = c("brown1", "black")) +
#     scale_fill_manual(values = c("brown1", "black")))
# summary(test_fits$mai.qb)
```

### Wrapper functions
```{r}
runTenureXOffspringModel <- function(surv_reg_data, survNom, survDen, tenure, treatment, quad = TRUE) {

  if (quad) {
    test_fits <- surv_reg_data %>%
      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
               survNom=survNom, survDen=survDen, quad = TRUE)
  } else if (!quad) {
    test_fits <- surv_reg_data %>%
      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
               survNom=survNom, survDen=survDen, quad = FALSE)
  }

  test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure=tenure, treatment=treatment,
                              survNom=survNom, survDen=survDen,
                              model = test_fits$mai.qb)

  p <- plot_ci(ci_data = test_ci_data, tenure = tenure, treatment=treatment,
                survNom = survNom, survDen = survDen) +
      xlab("Latest desertion date relative to hatch") +
      ylab("Hatching success") +
      scale_color_manual(values = c("brown1", "black")) +
      scale_fill_manual(values = c("brown1", "black"))
  stat_summary <- summary(test_fits$mai.qb)

  obj_out <- list(
    fits = test_fits,
    ci = test_ci_data,
    p = p,
    summary = stat_summary
  )
  return(obj_out)
}

# Example
# des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
#   runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
#                            tenure="des", treatment="ant_treatment")
```

# Supp 1 -`desL * ants_treatment * desL^2`
## Figures
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=des, treatment=ant_treatment)

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=des, treatment=ant_treatment)

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=des, treatment=ant_treatment)

(desL.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad$p +
                 theme(legend.position = c(0.8,0.95)) + 
                 ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ant_treatment.quad.final.png",
       desL.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

@@

```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

## Figures
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=des, treatment=ants_gt2d)

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=des, treatment=ants_gt2d)

# egg survivorship
des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=des, treatment=ants_gt2d)

(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ants_gt2d.quad.final.png",
       desL.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

# Supp 2 -`desP * ants_gt2 * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=desP, treatment=ants_gt2d)

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=desP, treatment=ants_gt2d)

# egg survivorship
des_Esurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=desP, treatment=ants_gt2d)

(desP.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ants_gt2d.quad.final.png",
       desP.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

# Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=desP, treatment=ant_treatment)

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=desP, treatment=ant_treatment)

# egg survivorship
des_Esurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=desP, treatment=ant_treatment)

(desP.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ant_treatment.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ant_treatment.quad.final.png",
       desP.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```
